---
title: "Problem Set 7"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Gapminder Code
This code is taken from PS02, which uses the a package called "gapminder". This package contains socioeconomic data about countries from 1952- 2007.
Here is the code to set up packages and our dataframe:

```{r, echo=TRUE}
#Loading Packages in
library(tidyverse)
library(gapminder)

#Now a bit of wrangling
gapminder_2007 <- gapminder %>% 
  filter(year == 2007)
```

## Gapminder Plot

And here is a scatterplot graph made with the dataframe above :

```{r plot, echo=FALSE}
ggplot(data = gapminder_2007, mapping = aes(x = gdpPercap, y = lifeExp, size = pop, color = continent)) + 
  geom_point()+
  labs(
    title = "Comparing GDP Per Capita to Life Expectancy in 2007",
    x = "GPD Per Capita in USD",
    y = "Life Expectancy in Years"
  )

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
